Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-12-03 paper/paper.tex

\author{Igor Lima \and Breno Miranda \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

\institute{Igor Lima \and \email{isol2@cin.ufpe.br} \\
Breno Miranda \and \email{bafm@cin.ufpe.br} \\
Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
\at Universidade Federal de Pernambuco, Recife, PE, Brazil}

@@

>>>>

\author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

\institute{
* Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
Igor Lima \and \email{isol2@cin.ufpe.br} \\
Breno Miranda \and \email{bafm@cin.ufpe.br} \\
Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
\at Universidade Federal de Pernambuco, Recife, PE, Brazil}

@@

%\institute{Corresponding author.}
